ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-08 paper.tex
fix image positions

\end{center}
\begin{flushright} % list your sponsors and advisers
	Atticus Sims, Sponsor \\
	Kyoto VR \par
	\vspace{\baselineskip}
	Professor Joshua Cuneo, Adviser \\
	Worcester Polytechnic Institute \par
	\vspace{\baselineskip}
	Professor Ralph Sutter, Adviser \\
	Worcester Polytechnic Institute \par
\end{flushright}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
	\caption{The ``Rename'' subcard}
	\label{fig:renameSubcard}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
	\caption{The ``Media'' subcard}
	\label{fig:mediaSubcard}
\end{figure}

The third subcard is the ``Points'' subcard. This subcard can be revealed in one
of two ways. The first way is by clicking on the yellow bar labeled ``Points'',
which is the same for all subcards. Alternatively, the user can click directly
on the region on the map. The region will flash yellow and be scrolled into view
to let the user know which region was clicked on. Both of these methods will
enable editing mode, whereby the user can directly manipulate the vertices that
make up the region. Blue circles appear on top of each vertex, and red circles
appear at the midpoint of each edge. Clicking on a red midpoint will add an
additional vertex at that midpoint. Dragging one of the blue vertices will move
the vertex around. The latitude and longitude are updated in the ``Points''
subcard as the user moves the vertex. Clicking on the vertex directly will
create a blue pin-shaped marker that the user can also drag. Clicking on the
coordinate box in the subcard will also create this blue pin-shaped marker; the
map will also pan to this coordinate. The user can also delete vertices in the
same way that files can be deleted from the ``Media'' subcard by clicking on the
`X' button on that vertex's coordinate card. If there are exactly three points
in a region, the `X' buttons will be ``grayed-out,'' preventing the user from
deleting any more points, since a polygon must consist of at least three points.

@@

When the page is loaded, the frontend will request the names of the tour files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. This feature
can be seen in figure Figure~\ref{fig:downloadCard}. Clicking ``Download'' does
not download the tour to the user's computer. Instead, it requests only the
tour metadata from the server so the tour's data can be displayed in the web
app. The user can then edit the tour and upload a new version.

@@

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button to pan to the specified location. We also hard-coded a few
shortcuts for places that Atticus might want to design a tour for in the future,
which can be accessed by clicking on the yellow buttons with place names.

@@

The look and feel of the Editour frontend was inspired from multiple sources.
The color scheme of the UI was inspired by the Super Famicom controller, which
can be seen in Figure~\ref{fig:superFamicomController}. The shape of the
``cards'' within the sidebar were inspired by the GitHub Kanban board on the
``Projects'' tab of a GitHub repo (which can be seen in
Figure~\ref{fig:kanbanBoard} in the Appendix).

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating and can
produce poor results. Google~Translate's text recognition and machine-learning
powered translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. This will sometimes produce useless
results, as seen in Figure~\ref{fig:translateInstant}. Then, the user is
prompted to highlight where text appears in the photo by dragging lines onto the
screen where text appears, as seen in Figure~\ref{fig:translateScan}. After the
translation is complete, the translated text appears in a separate UI element,
which can be seen in Figure~\ref{fig:translateFinalCard}. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable text box. This motivated the current design of the ``info buttons''
in ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized ``\textit{i}'' in the center. By tapping on this button, a
separate UI element will appear containing the translated text. Since this
button is cast into the world using the AR camera, the button appears to be
placed directly on top of the content.

% TODO make it so these images don't appear so far away (thank you LaTeX)
\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-instant.jpg}
	\caption{Google Translate camera feature in ``instant'' mode.}
	\label{fig:translateInstant}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-scan.jpg}
	\caption{Google Translate camera feature in ``scan'' mode}
	\label{fig:translateScan}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-final-card.png}
	\caption{The final page seen after using ``scan'' mode in Google Translate}
	\label{fig:translateFinalCard}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{souvenir.png}
	\caption{ARuko's virtual souvenir feature}
	\label{fig:souvenir}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{kinkakuji-horizontal.png}
	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
	\label{fig:kinkakujiHorizontal}
\end{figure}

@@

One of the notable changes is the chapter select screen, which is the third
screen in Figure~\ref{fig:adobeXdDesign}. Before, we worked under the assumption
that each geolocation-triggered region would not have to be ordered in any way.
This assumption made its way into Editour, which at the time did not have a way
to reorder regions once they were placed. Because of this chapter selection
screen, we needed some way to specify and rearrange the order of regions within
Editour.

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption{Additions to Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

With the ground-plane detection features stripped away from the main app, the AR
focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} and Figure~\ref{fig:infoZoomed} shows a
mock-up of this feature. Atticus took photographs of various signs throughout
Kinkaku-ji for us to use as image targets. Hikaru Inoue helped us by translating
all of the text in these photos from Japanese to English. In this design, the AR
camera superimposes an ``info'' button on top of the sign. Tapping on this
button brings up a separate UI element containing the translation, which can be
seen in Figure~\ref{fig:translationZoomed}. The details of this feature is
discussed more thoroughly in Section~\ref{sec:translationFeature}.

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{chapters-zoomed.png}
    \caption{Larger screenshot of the chapter selection screen mock-up}
    \label{fig:chaptersZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{gallery-zoomed.png}
    \caption{Larger screenshot of the transcript and image gallery mock-up}
    \label{fig:galleryZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{info-zoomed.png}
    \caption{Larger screenshot of the info button mock-up}
    \label{fig:infoZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{map-zoomed.png}
    \caption{Larger screenshot of the route screen mock-up}
    \label{fig:mapZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{translation-zoomed.png}
    \caption{Larger screenshot of the translation window mock-up}
    \label{fig:translationZoomed}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkaku-ji tour]{The original version
		of the Kinkaku-ji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
		version of the Kinkaku-ji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

@@

We also noticed that we were only able to augment a maximum of two image targets
at a time. In almost all cases, only two translatable signs were in view at
once. The only scenario in which there were more than two image targets in view
at a given time was with the four framed photos of the interior, which were
arranged in a two by two grid. When standing at a distance from the grid, only
two images would be augmented with the blue information button. By default,
Vuforia limits the amount of image targets that the engine should accept
simultaneously. In the Vuforia engine settings, we changed this limit to
accommodate for four simultaneous images.

@@

Atticus Sims proposed the idea of working with Michael Whittle, a British artist
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo and group exhibitions across the world,
including Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}.
Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
solo exhibition, \textit{Portraits of Thought}. This exhibition displayed diagrams
inspired by real science and mathematics. Atticus provided us with some
diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
to know how well certain pieces of art would work as AR image targets. All of
images that were provided to us were ranked as ``five stars'' by Vuforia,
indicating that those images would serve well as AR image targets.

>>>>

\end{center}
\begin{flushright} % list your sponsors and advisers
	Atticus Sims, Sponsor \\
	Kyoto VR \par
	\vspace{\baselineskip}
	Professor Ralph Sutter, Adviser \\
	Worcester Polytechnic Institute \par
	\vspace{\baselineskip}
	Professor Joshua Cuneo, Adviser \\
	Worcester Polytechnic Institute \par
\end{flushright}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
	\caption{The ``Rename'' subcard}
	\label{fig:renameSubcard}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
	\caption{The ``Media'' subcard}
	\label{fig:mediaSubcard}
\end{figure}

@@

The third subcard is the ``Points'' subcard. This subcard can be revealed in one
of two ways. The first way is by clicking on the yellow bar labeled ``Points'',
which is the same for all subcards. Alternatively, the user can click directly
on the region on the map. The region will flash yellow and be scrolled into view
to let the user know which region was clicked on. Both of these methods will
enable editing mode, whereby the user can directly manipulate the vertices that
make up the region. Blue circles appear on top of each vertex, and red circles
appear at the midpoint of each edge. Clicking on a red midpoint will add an
additional vertex at that midpoint. Dragging one of the blue vertices will move
the vertex around. The latitude and longitude are updated in the ``Points''
subcard as the user moves the vertex. Clicking on the vertex directly will
create a blue pin-shaped marker that the user can also drag (see
Figure~\ref{fig:editSubcardWithMap}). Clicking on the coordinate box in the
subcard will also create this blue pin-shaped marker; the map will also pan to
this coordinate. The user can also delete vertices in the same way that files
can be deleted from the ``Media'' subcard by clicking on the `X' button on that
vertex's coordinate card. If there are exactly three points in a region, the `X'
buttons will be ``grayed-out,'' preventing the user from deleting any more
points, since a polygon must consist of at least three points.

@@

When the page is loaded, the frontend will request the names of the tour files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. This feature
can be seen in Figure~\ref{fig:downloadCard}. Clicking ``Download'' does
not download the tour to the user's computer. Instead, it requests only the
tour metadata from the server so the tour's data can be displayed in the web
app. The user can then edit the tour and upload a new version.

@@

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins or libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button to pan to the specified location. We also hard-coded a few
shortcuts for places that Atticus might want to design a tour for in the future,
which can be accessed by clicking on the yellow buttons with place names.

@@

The look and feel of the Editour frontend was inspired from multiple sources.
The color scheme of the UI was inspired by the Super Famicom controller, which
can be seen in Figure~\ref{fig:superFamicomController}. The shape of the
``cards'' within the sidebar were inspired by the GitHub Kanban board on the
``Projects'' tab of a GitHub repo (which can be seen in
Figure~\ref{fig:kanbanBoard} in Appendix~\ref{sec:versionControl}).

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating and can
produce poor results. Google~Translate's text recognition and machine-learning
powered translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. This will sometimes produce useless
results, as seen in Figure~\ref{fig:translateInstant}. Then, the user is
prompted to highlight where text appears in the photo by dragging lines onto the
screen where text appears, as seen in Figure~\ref{fig:translateScan}. After the
translation is complete, the translated text appears in a separate UI element.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{translate-instant.jpg}
	\caption{Google Translate camera feature in ``instant'' mode.}
	\label{fig:translateInstant}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{translate-scan.jpg}
	\caption{Google Translate camera feature in ``scan'' mode}
	\label{fig:translateScan}
\end{figure}

In most cases, it is more convenient and readable to have the translation appear
in a separate scrollable text box. This motivated the current design of the
``info buttons'' in ARuko. Instead of placing text directly onto signage, we
place a blue button with a stylized ``\textit{i}'' in the center. By tapping on
this button, a separate UI element will appear containing the translated text.
Since this button is cast into the world using the AR camera, the button appears
to be placed directly on top of the content.

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=.8\textwidth]{souvenir.png}
	\caption{ARuko's virtual souvenir feature}
	\label{fig:souvenir}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=.8\textwidth]{kinkakuji-horizontal.png}
	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
	\label{fig:kinkakujiHorizontal}
\end{figure}

@@

One of the notable changes is the chapter select screen, which is the third
screen in Figure~\ref{fig:adobeXdDesign} and in Figure~\ref{fig:chaptersZoomed}.
Before, we worked under the assumption that each geolocation-triggered region
would not have to be ordered in any way. This assumption made its way into
Editour, which at the time did not have a way to reorder regions once they were
placed. Because of this chapter selection screen, we needed some way to specify
and rearrange the order of regions within Editour.

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{chapters-zoomed.png}
    \caption{Larger screenshot of the chapter selection screen mock-up}
    \label{fig:chaptersZoomed}
\end{figure}

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{gallery-zoomed.png}
    \caption{Larger screenshot of the transcript and image gallery mock-up}
    \label{fig:galleryZoomed}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.3\textwidth]{editour-additions.png}
	\caption{Additions to Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

With the ground-plane detection features stripped away from the main app, the AR
focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} and
Figure~\ref{fig:infoTranslationZoomed} shows a mock-up of this feature.

\begin{figure}[p] \centering
    \includegraphics[width=0.8\textwidth]{info-translation-zoomed.png}
    \caption{Larger screenshot of the info button and translation mock-up}
    \label{fig:infoTranslationZoomed}
\end{figure}

Atticus took photographs of various signs throughout
Kinkaku-ji for us to use as image targets. Hikaru Inoue helped us by translating
all of the text in these photos from Japanese to English. In this design, the AR
camera superimposes an ``info'' button on top of the sign. Tapping on this
button brings up a separate UI element containing the translation, which can be
seen in Figure~\ref{fig:infoTranslationZoomed}. The details of this feature is
discussed more thoroughly in Section~\ref{sec:translationFeature}.

Another feature that was added was the ability for the user to preview the
route. Figure~\ref{fig:mapZoomed} shows the map screen of the app. The map
screen is simply a static image that can be pinched and zoomed.

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{map-zoomed.png}
    \caption{Larger screenshot of the route screen mock-up}
    \label{fig:mapZoomed}
\end{figure}

@@

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkaku-ji tour]{The original version
		of the Kinkaku-ji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
		version of the Kinkaku-ji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

@@

We also noticed that we were only able to augment a maximum of two image targets
at a time. In almost all cases, only two translatable signs were in view at
once. The only scenario in which there were more than two image targets in view
at a given time was with the four framed photos of the interior, which were
arranged in a two by two grid. When standing at a distance from the grid, only
two images would be augmented with the blue information button. By default,
Vuforia limits the amount of image targets that the engine should accept
simultaneously. In the Vuforia engine settings, we changed this limit to
accommodate for four simultaneous images (see Figure~\ref{fig:fourIButtons}).

@@

Atticus Sims proposed the idea of working with Michael Whittle, a British artist
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo and group exhibitions across the world, including
Kyoto, Beijing, London, and New York~\autocite{michaelwhittle2019}. Kyoto~VR has
worked with Michael Whittle in the past to create a 3D scan of a solo
exhibition, \textit{Portraits of Thought} (Figure~\ref{fig:exhibitionScan}).
This exhibition displayed diagrams inspired by real science and mathematics.
Atticus provided us with some diagrams to test in the Vuforia developer portal,
since Michael Whittle wanted to know how well certain pieces of art would work
as AR image targets. All of images that were provided to us were ranked as
``five stars'' by Vuforia, indicating that those images would serve well as AR
image targets.
